### 2014-12-30 ThesisJo/introduction.tex
la2pdf commit - 2014:10:27	16:25:27	(Mon27.Oct)
Some KM presentation files added

@@

@@

% \begin{align*}
% \nabla^2 g(\p,t) - \frac{1}{c^2(\p)}
% \end{align*}

% where $\nabla^2$ is the Laplacian operator

>>>>

The best processing unit we know of is the human mind. Its several billion neurons process information at a staggering rate, and concurrently. As described by this year's nobel price winners, memories of visual objects gets stored in a similar spacial structure in the brain.

Similar to how the process visual input from our eyes and turn them into the images we perceive, we want turn echo from sonar systems into images of the physical objects the sound was scattered by.

Want to compare acoustic array to the eyes. Similar, this images from sound should be possible. Brain parallel, and superior. Thus, processing power must be essential to the continued improvement of current sonar systems. But *how* should be additional processing power be used?

Signal processing is the art of combining physics, mathematics and computational engineering

@@

\chapter{Introduction}

@@

\begin{align*}
\nabla^2 f(\p,t) - \frac{1}{c^2(\p)}\frac{\partial^2 f(\p,t)}{\partial t^2} = -s(t) \delta(\p-\p_0)
\end{align*}

where $\nabla^2$ is the Laplacian operator
